\textls[-0]{\thetitle}

### 2023-03-04 introduction.tex
Add a comment macro for each reviewer

The EP is well studied in the conventional setting of functional
programming and object-oriented (OO) programming.
Modern languages, such as Scala \cite{scala-oopsla05}, have a good
supply of linguistic features that offer expressive power to solve the
EP.

>>>>

The EP is well studied in the conventional setting of functional
programming and object-oriented (OO) programming.
Modern languages, such as Scala \cite{scala-oopsla05}, have a good
supply of linguistic features that offer expressive power to solve the
EP.\rD{There is no shortage of solutions to the EP in various
languages, but there are no citations to those works.}
